HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-11 paper/main.tex
for camera ready

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small ... don't skip meals ... \\
Transl.& \small ... nicht {\"u}berspringen Mahlzeiten ... \\
Gloss & \small don't skip meals ... \\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small ... tend to be higher in saturated fats \\
Transl.& \small in der Regel h{\"o}her in ges{\"a}ttigte Fette \\
Gloss & \small as a rule higher in saturated fats \\
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small ... don't skip meals ... \\
Transl.& \small ... nicht {\"u}berspringen Mahlzeiten ... \\
Gloss & \small ... don't skip meals ... \\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small ... tend to be higher in saturated fats \\
Transl.& \small ... in der Regel h{\"o}her in ges{\"a}ttigte Fette \\
Gloss & \small ... as a rule higher in saturated fats \\
\end{tabular}
\end{center}
